LDATS changepoint

### 2019-01-08 paper-comparison/ldats_changepoint.Rmd
Report changepoint estimates as dates

rm(list = c('dat', 'dates', 'period_dates', 'moondat',
            'create_rodent_table'))

@@

```{r show ldats lda + ldats cpt}
plot(ldats_ldats_cpt_selected)
ldats_ldats_cpt_selected$formula
ldats_ldats_cpt_selected$nchangepoints
ldats_ldats_cpt_selected$rho_summary
```

@@

```{r show paper lda + ldats cpt}
plot(paper_ldats_cpt_selected)
paper_ldats_cpt_selected$formula
paper_ldats_cpt_selected$nchangepoints
paper_ldats_cpt_selected$rho_summary
```

>>>>

rm(list = c('dat', 'dates',
            'create_rodent_table'))

@@

```{r show ldats lda + ldats cpt}
plot(ldats_ldats_cpt_selected)
ldats_ldats_cpt_selected$formula
ldats_ldats_cpt_selected$nchangepoints
cpt_means <- ldats_ldats_cpt_selected$rho_summary$Mean

cpt_means <- floor(cpt_means)
cpt_means <- as.data.frame(cpt_means)
colnames(cpt_means) <- 'newmoonnumber'
cpt_means$cpt <- 1:ldats_ldats_cpt_selected$nchangepoints

cpt_dates <- as.data.frame(moondat) %>%
  dplyr::select(newmoonnumber, newmoondate) %>%
  dplyr::left_join(cpt_means, by = 'newmoonnumber') %>%
  dplyr::filter(!is.na(cpt))

cpt_dates

@@

```{r show paper lda + ldats cpt}
plot(paper_ldats_cpt_selected)
paper_ldats_cpt_selected$formula
paper_ldats_cpt_selected$nchangepoints
cpt_means <- paper_ldats_cpt_selected$rho_summary$Mean

cpt_means <- floor(cpt_means)
cpt_means <- as.data.frame(cpt_means)
colnames(cpt_means) <- 'newmoonnumber'
cpt_means$cpt <- 1:paper_ldats_cpt_selected$nchangepoints

cpt_dates <- as.data.frame(moondat) %>%
  dplyr::select(newmoonnumber, newmoondate) %>%
  dplyr::left_join(cpt_means, by = 'newmoonnumber') %>%
  dplyr::filter(!is.na(cpt))

cpt_dates
```
